Chatbots in the classroom: an analysis from the teacher's perspective

### 2021-05-16 edubots_surveys.Rnw
adds new works to state of the art refs #6
adds chatbot categories and adoption factors refs #6

Regarding the factors for the adoption of chatbots in Education, many studies have focused on the evaluation of technology acceptance or usability. However, Higher Education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.

>>>>

% Categorization and examples of what they can do, adapted to questions in the survey   
A possible categorization of chatbots in Education splits them according to their purpose into service- and teaching-oriented \cite{perez2020rediscovering}. The first class includes chatbots that provide service support used e.g. to solve questions about the enrollment \cite{santoso2018dinus}, registration, or academic requirements for exchange students \cite{ranoliya2017chatbot}. Focusing on the use at class, service-oriented chatbots would help to introduce students to each other (as done with LISA \cite{dibitonto2018chatbot}), would provide information about schedules and deadlines, recommend general learning materials for the next classes, or individually inform about grades. Teaching-oriented chatbots are more sophisticated chatbots that set goals and monitor learning progress. A simple example is described in \cite{coronado2018cognitive} where authors proposed agents that store learning materials to be provided on demand to students. Also, more complex tutoring systems \cite{crockett2017predicting} individually analyze the learning state of students to provide the next most suitable material in their learning path.

% Point: chatbots are accepted if they help to achieve learning goals
Regarding the factors for the adoption of chatbots in Education, many studies have focused on the evaluation of technology acceptance or usability such as \cite{Pimmer2019, Roblyer2010}. However, Higher Education is a special domain where according to \cite{hobert2019you}, specific pedagogical factors such as learning success or increased motivation are more important.
